Research paper

### 2012-11-21 Research paper.tex
Added another strength

\subsubsection{The theory is tested immediately}

>>>>

\subsubsection{The theory is tested immediately and completely}

An idea is very different from something that is really useful or true. Many fields of science get stuck somewhere in this transition. In some fields scholars only write down their ideas in human language, not fully formulating how the idea should work, and thus never discovering there might be flaws in the idea somewhere. In other fields scholars can make the idea formal, but have no way to test the ideas in any other way than trusting on intuitions. In again other fields one can test it, for example by means of experiments, but it remains unclear how the results should be interpreted and to what extent they generalize to the whole population. All this is not a problem for the Colibri project. Claims are made (for example 'skipgrams improve machine translation'), formalized ('this is how they should work within in a machine translation system'), but also implemented and fully tested (i.e. in a fully functional machine learning system). In other words, except maybe for the evaluation measures, there is little reason to doubt the results of this project.
